```{r Global, echo=FALSE, warning=FALSE, message=FALSE}
source("Global.R")
DF_674 <- DF_674 %>% 
  filter(dx_spot == "Invasive") %>% 
  droplevels()

DF_931 <- DF_931 %>% 
  filter(dx_spot == "Invasive") %>% 
  droplevels()

```

\   

# By maximum SFXN1 intensity {.tabset .tabset-pills .tabset-fade}
## TMA 674 {.tabset .tabset-pills .tabset-fade}
```{r DF_674}
DF <- DF_674
x <- DF$SFXN1_int_max
```

### Clinical features {.tabset .tabset-pills .tabset-fade}
#### Age
```{r age_group.DF_674}
y <- DF$age_group
g2_nice(x, y)
tbl_nice(x, y)
tbl_test(x, y)
```

#### Sex
```{r sex.DF_674}
y <- DF$sex
g2_nice(x, y)
tbl_nice(x, y)
tbl_test(x, y)
```

#### Race
```{r race.DF_674}
y <- DF$race
g2_nice(x, y)
tbl_nice(x, y)
tbl_test(x, y)
```

### Pathologic features {.tabset .tabset-pills .tabset-fade}
#### Pathologic stage
```{r stage_pt.DF_674}
y <- DF$stage_pt
g2_nice(x, y)
tbl_nice(x, y)
tbl_test(x, y)
```

#### Clinical stage
```{r stage_clinical.DF_674}
y <- DF$stage_clinical
g2_nice(x, y)
tbl_nice(x, y)
tbl_test(x, y)
```

#### Adjacent CIS
```{r CIS.DF_674}
y <- DF$CIS
g2_nice(x, y)
tbl_nice(x, y)
tbl_test(x, y)
```

#### Lymphovascular invasion
```{r lvi.DF_674}
y <- DF$lvi
g2_nice(x, y)
tbl_nice(x, y)
tbl_test(x, y)
```

#### Lymph node metastasis
```{r metastasis_lymph.DF_674}
y <- DF$metastasis_lymph
g2_nice(x, y)
tbl_nice(x, y)
tbl_test(x, y)
```

### Outcome features {.tabset .tabset-pills .tabset-fade}
#### Tumor progression
```{r progression.DF_674}
y <- DF$progression
g2_nice(x, y)
tbl_nice(x, y)
tbl_test(x, y)
```

#### Visceral metastasis
```{r metastasis_visceral.DF_674}
y <- DF$metastasis_visceral
g2_nice(x, y)
tbl_nice(x, y)
tbl_test(x, y)
```

#### Overall mortality
```{r dead.DF_674}
y <- DF$dead
g2_nice(x, y)
tbl_nice(x, y)
tbl_test(x, y)
```

#### Cancer-related mortality
```{r dod.DF_674}
y <- DF$dod
g2_nice(x, y)
tbl_nice(x, y)
tbl_test(x, y)
```

## TMA 931 {.tabset .tabset-pills .tabset-fade}
```{r DF_931}
DF <- DF_931
x <- DF$SFXN1_int_max
```

### Clinical features {.tabset .tabset-pills .tabset-fade}
#### Age
```{r age_group.DF_931}
y <- DF$age_group
g2_nice(x, y)
tbl_nice(x, y)
tbl_test(x, y)
```

#### Sex
```{r sex.DF_931}
y <- DF$sex
g2_nice(x, y)
tbl_nice(x, y)
tbl_test(x, y)
```

### Pathologic features {.tabset .tabset-pills .tabset-fade}
#### Pathologic stage
```{r stage_pt.DF_931}
y <- DF$stage_pt
g2_nice(x, y)
tbl_nice(x, y)
tbl_test(x, y)
```

### Outcome features {.tabset .tabset-pills .tabset-fade}
#### Tumor recurrence
```{r recurrence.DF_931}
y <- DF$recurrence
g2_nice(x, y)
tbl_nice(x, y)
tbl_test(x, y)
```

#### Tumor progression
```{r progression.DF_931}
y <- DF$progression
g2_nice(x, y)
tbl_nice(x, y)
tbl_test(x, y)
```

#### Overall mortality
```{r dead.DF_931}
y <- DF$dead
g2_nice(x, y)
tbl_nice(x, y)
tbl_test(x, y)
```
