```{r Global, echo=FALSE, warning=FALSE, message=FALSE}
source("Global.R")
```

\   

# Clinicopathologic and outcome features {.tabset .tabset-pills .tabset-fade}
## TMA 674 {.tabset .tabset-pills .tabset-fade}
### Clinical features {.tabset .tabset-pills .tabset-fade}
#### Age
```{r age.DF_674}
x <- DF_674$age
g_nice(x, max_break = 90)
tbl_nice(x)
```

#### Sex
```{r sex.DF_674}
x <- DF_674$sex
g_nice(x)
tbl_nice(x)
```

#### Race
```{r race.DF_674}
x <- DF_674$race
g_nice(x)
tbl_nice(x)
```

### Pathologic features {.tabset .tabset-pills .tabset-fade}
#### Diagnosis
```{r dx_spot.DF_674}
x <- DF_674$dx_spot
g_nice(x)
tbl_nice(x)
```

#### pT stage
```{r stage_pt.DF_674}
x <- DF_674$stage_pt
g_nice(x)
tbl_nice(x)
```

#### Clinical stage
```{r stage_clinical.DF_674}
x <- DF_674$stage_clinical
g_nice(x)
tbl_nice(x)
```

#### Histologic grade
```{r grade.DF_674}
x <- DF_674$grade
g_nice(x)
tbl_nice(x)
```

#### CIS
```{r CIS.DF_674}
x <- DF_674$CIS
g_nice(x)
tbl_nice(x)
```

#### Lymphovascular invasion
```{r lvi.DF_674}
x <- DF_674$lvi
g_nice(x)
tbl_nice(x)
```

#### Lymph node metastasis
```{r metastasis_lymph.DF_674}
x <- DF_674$metastasis_lymph
g_nice(x)
tbl_nice(x)
```

### Preoperative features {.tabset .tabset-pills .tabset-fade}
#### Preop CIS
```{r preop_cis.DF_674}
x <- DF_674$preop_cis
g_nice(x)
tbl_nice(x)
```

#### Preop procedure
```{r preop_procedure.DF_674}
x <- DF_674$preop_procedure
g_nice(x)
tbl_nice(x)
```

#### Preop stage
```{r preop_stage.DF_674}
x <- DF_674$preop_stage
g_nice(x)
tbl_nice(x)
```

### Treatment features {.tabset .tabset-pills .tabset-fade}
#### Preop RTx
```{r preop_rtx.DF_674}
x <- DF_674$preop_rtx
g_nice(x)
tbl_nice(x)
```

#### Preop CTx
```{r preop_ctx.DF_674}
x <- DF_674$preop_ctx
g_nice(x)
tbl_nice(x)
```

#### Intravesical CTx
```{r intravesical_ctx.DF_674}
x <- DF_674$intravesical_ctx
g_nice(x)
tbl_nice(x)
```

#### Intravesical CTx type
```{r intravesical_ctx_type.DF_674}
x <- DF_674$intravesical_ctx_type
g_nice(x)
tbl_nice(x)
```

#### Postop RTx
```{r postop_rtx.DF_674}
x <- DF_674$postop_rtx
g_nice(x)
tbl_nice(x)
```

#### Postop CTx
```{r postop_ctx}
x <- DF_674$postop_ctx
g_nice(x)
tbl_nice(x)
```

#### Postop CTx type
```{r postop_ctx_type.DF_674}
x <- DF_674$postop_ctx_type
g_nice(x)
tbl_nice(x)
```

### Outcome features {.tabset .tabset-pills .tabset-fade}
#### Follow-up, in months
```{r fu_months.DF_674}
x <- DF_674$fu_months
g_nice(x, bin = 24)
tbl_nice(x)
```

#### Tumor progression
```{r progression.DF_674}
x <- DF_674$progression
g_nice(x)
tbl_nice(x)
```

#### Visceral metastasis
```{r metastasis_visceral.DF_674}
x <- DF_674$metastasis_visceral
g_nice(x)
tbl_nice(x)
```

#### Overall mortality
```{r dead.DF_674}
x <- DF_674$dead
g_nice(x)
tbl_nice(x)
```

#### Cancer-related mortality
```{r dod.DF_674}
x <- DF_674$dod
g_nice(x)
tbl_nice(x)
```


## TMA 931 {.tabset .tabset-pills .tabset-fade}
### Clinical features {.tabset .tabset-pills .tabset-fade}
#### Age
```{r age.DF_931}
x <- DF_931$age
g_nice(x, max_break = 90)
tbl_nice(x)
```

#### Sex
```{r sex.DF_931}
x <- DF_931$sex
g_nice(x)
tbl_nice(x)
```

### Pathologic features {.tabset .tabset-pills .tabset-fade}
#### Diagnosis
```{r dx_spot.DF_931}
x <- DF_931$dx_spot
g_nice(x)
tbl_nice(x)
```

#### pT stage
```{r stage_pt.DF_931}
x <- DF_931$stage_pt
g_nice(x)
tbl_nice(x)
```

```{r grade.DF_931}
#### Histologic grade
# x <- DF_674$grade
# g_nice(x)
# tbl_nice(x)
```

### Treatment features {.tabset .tabset-pills .tabset-fade}
#### Intravesical CTx
```{r intravesical_ctx.DF_931}
x <- DF_931$intravesical_ctx
g_nice(x)
tbl_nice(x)
```

#### Intravesical CTx type
```{r intravesical_ctx_type.DF_931}
x <- DF_931$intravesical_ctx_type
g_nice(x)
tbl_nice(x)
```

### Outcome features {.tabset .tabset-pills .tabset-fade}
#### Follow-up, in months
```{r fu_months.DF_931}
x <- DF_931$fu_months
g_nice(x, bin = 24)
tbl_nice(x)
```

#### Tumor recurrence
```{r recurrence.DF_931}
x <- DF_931$recurrence
g_nice(x)
tbl_nice(x)
```

#### Tumor progression
```{r progression.DF_931}
x <- DF_931$progression
g_nice(x)
tbl_nice(x)
```

#### Overall mortality
```{r dead.DF_931}
x <- DF_931$dead
g_nice(x)
tbl_nice(x)
```
