```{r Global, echo=FALSE, warning=FALSE, message=FALSE}
source("Global.R")
```

\   

# Marker features {.tabset .tabset-pills .tabset-fade}
## TMA 674 {.tabset .tabset-pills .tabset-fade}
```{r SFXN1_674}
marker <- SFXN1_674
```

### By TMA spots {.tabset .tabset-pills .tabset-fade}
#### Marker extent
```{r SFXN1_extent.SFXN1_674}
x <- marker$SFXN1_ext
g_nice(x, bin = 10)
tbl_nice(x)
```

#### Marker intensity
```{r SFXN1_intensity.SFXN1_674}
x <- factor(marker$SFXN1_int)
g_nice(x)
tbl_nice(x)
```

#### Marker H-score
```{r SFXN1_h.SFXN1_674}
x <- marker$SFXN1_h
g_nice(x, bin = 25)
tbl_nice(x)
```

### By SP cases {.tabset .tabset-pills .tabset-fade}
```{r DF_674}
DF <- DF_674
```

#### By median value {.tabset .tabset-pills .tabset-fade}
##### Marker extent
```{r SFXN1_ext_med.DF_674}
x <- DF$SFXN1_ext_med
g_nice(x, bin = 10)
tbl_nice(x)
```

##### Marker intensity
```{r SFXN1_int_med.DF_674}
x <- factor(DF$SFXN1_int_med)
g_nice(x)
tbl_nice(x)
```

##### Marker H-score
```{r SFXN1_h_med.DF_674}
x <- DF$SFXN1_h_med
g_nice(x, bin = 25)
tbl_nice(x)
```

#### By maximum value {.tabset .tabset-pills .tabset-fade}
##### Marker extent
```{r SFXN1_ext_max.DF_674}
x <- DF$SFXN1_ext_max
g_nice(x, bin = 10)
tbl_nice(x)
```

##### Marker intensity
```{r SFXN1_int_max.DF_674}
x <- factor(DF$SFXN1_int_max)
g_nice(x)
tbl_nice(x)
```

##### Marker H-score
```{r SFXN1_h_max.DF_674}
x <- DF$SFXN1_h_max
g_nice(x, bin = 25)
tbl_nice(x)
```

## TMA 931 {.tabset .tabset-pills .tabset-fade}
```{r SFXN1_931}
marker <- SFXN1_931
```

### By TMA spots {.tabset .tabset-pills .tabset-fade}
#### Marker extent
```{r SFXN1_extent.SFXN1_931}
x <- marker$SFXN1_ext
g_nice(x, bin = 10)
tbl_nice(x)
```

#### Marker intensity
```{r SFXN1_intensity.SFXN1_931}
x <- factor(marker$SFXN1_int)
g_nice(x)
tbl_nice(x)
```

#### Marker H-score
```{r SFXN1_h.SFXN1_931}
x <- marker$SFXN1_h
g_nice(x, bin = 25)
tbl_nice(x)
```

### By SP cases {.tabset .tabset-pills .tabset-fade}
```{r DF_931}
DF <- DF_931
```

#### By median value {.tabset .tabset-pills .tabset-fade}
##### Marker extent
```{r SFXN1_ext_med.DF_931}
x <- DF$SFXN1_ext_med
g_nice(x, bin = 10)
tbl_nice(x)
```

##### Marker intensity
```{r SFXN1_int_med.DF_931}
x <- factor(DF$SFXN1_int_med)
g_nice(x)
tbl_nice(x)
```

##### Marker H-score
```{r SFXN1_h_med.DF_931}
x <- DF$SFXN1_h_med
g_nice(x, bin = 25)
tbl_nice(x)
```

#### By maximum value {.tabset .tabset-pills .tabset-fade}
##### Marker extent
```{r SFXN1_ext_max.DF_931}
x <- DF$SFXN1_ext_max
g_nice(x, bin = 10)
tbl_nice(x)
```

##### Marker intensity
```{r SFXN1_int_max.DF_931}
x <- factor(DF$SFXN1_int_max)
g_nice(x)
tbl_nice(x)
```

##### Marker H-score
```{r SFXN1_h_max.DF_931}
x <- DF$SFXN1_h_max
g_nice(x, bin = 25)
tbl_nice(x)
```
