```{r Global, echo=FALSE, warning=FALSE, message=FALSE}
source("Global.R")
```

\   

# Survival curves {.tabset .tabset-pills .tabset-fade}
## TMA 674 {.tabset .tabset-pills .tabset-fade}
```{r DF_674}
DF <- DF_674 %>% 
  filter(dx_spot == "Invasive") %>% 
  droplevels()

FU <- DF$fu_months
```

### Tumor progression {.tabset .tabset-pills .tabset-fade}
```{r progression.DF_674}
outcome <- DF$progression
```

#### By extent
```{r SFXN1_ext_level_med.progression.DF_674}
status <- DF$SFXN1_ext_level_med
g_surv(FU, outcome, status)
```

#### By intensity
```{r SFXN1_int_level_med.progression.DF_674}
status <- DF$SFXN1_int_level_med
g_surv(FU, outcome, status)
```

#### By H-score
```{r SFXN1_h_level_med.progression.DF_674}
status <- DF$SFXN1_h_level_med
g_surv(FU, outcome, status)
```

### Overall mortality {.tabset .tabset-pills .tabset-fade}
```{r dead.DF_674}
outcome <- DF$dead
```

#### By extent
```{r SFXN1_ext_level_med.dead.DF_674}
status <- DF$SFXN1_ext_level_med
g_surv(FU, outcome, status)
```

#### By intensity
```{r SFXN1_int_level_med.dead.DF_674}
status <- DF$SFXN1_int_level_med
g_surv(FU, outcome, status)
```

#### By H-score
```{r SFXN1_h_level_med.dead.DF_674}
status <- DF$SFXN1_h_level_med
g_surv(FU, outcome, status)
```

### Cancer-related mortality {.tabset .tabset-pills .tabset-fade}
```{r dod.DF_674}
outcome <- DF$dod
```

#### By extent
```{r SFXN1_ext_level_med.dod.DF_674}
status <- DF$SFXN1_ext_level_med
g_surv(FU, outcome, status)
```

#### By intensity
```{r SFXN1_int_level_med.dod.DF_674}
status <- DF$SFXN1_int_level_med
g_surv(FU, outcome, status)
```

#### By H-score
```{r SFXN1_h_level_med.dod.DF_674}
status <- DF$SFXN1_h_level_med
g_surv(FU, outcome, status)
```

## TMA 931 {.tabset .tabset-pills .tabset-fade}
```{r DF_931}
DF <- DF_931 %>% 
  filter(dx_spot == "Invasive") %>% 
  droplevels()

FU <- DF$fu_months
```

### Tumor recurrence {.tabset .tabset-pills .tabset-fade}
```{r recurrence.DF_931}
outcome <- DF$recurrence
```

#### By extent
```{r SFXN1_ext_level_med.recurrence.DF_931}
status <- DF$SFXN1_ext_level_med
g_surv(FU, outcome, status)
```

#### By intensity
```{r SFXN1_int_level_med.recurrence.DF_931}
status <- DF$SFXN1_int_level_med
g_surv(FU, outcome, status)
```

#### By H-score
```{r SFXN1_h_level_med.recurrence.DF_931}
status <- DF$SFXN1_h_level_med
g_surv(FU, outcome, status)
```

### Tumor progression {.tabset .tabset-pills .tabset-fade}
```{r progression.DF_931}
outcome <- DF$progression
```

#### By extent
```{r SFXN1_ext_level_med.progression.DF_931}
status <- DF$SFXN1_ext_level_med
g_surv(FU, outcome, status)
```

#### By intensity
```{r SFXN1_int_level_med.progression.DF_931}
status <- DF$SFXN1_int_level_med
g_surv(FU, outcome, status)
```

#### By H-score
```{r SFXN1_h_level_med.progression.DF_931}
status <- DF$SFXN1_h_level_med
g_surv(FU, outcome, status)
```

### Overall mortality {.tabset .tabset-pills .tabset-fade}
```{r dead.DF_931}
outcome <- DF$dead
```

#### By extent
```{r SFXN1_ext_level_med.dead.DF_931}
status <- DF$SFXN1_ext_level_med
g_surv(FU, outcome, status)
```

#### By intensity
```{r SFXN1_int_level_med.dead.DF_931}
status <- DF$SFXN1_int_level_med
g_surv(FU, outcome, status)
```

#### By H-score
```{r SFXN1_h_level_med.dead.DF_931}
status <- DF$SFXN1_h_level_med
g_surv(FU, outcome, status)
```
